\chapter{Task 1}
\begin{itemize}
	\item Architectural levels provide an abstraction method for Software Architectures, they are organised in an hierarchical order. Starting from the fundamental building block of the architecture the level of abstraction increases. The distinction from one level to another allows software architects to address different problems at different levels, and to avoid mixing these different aspects. Creating this structure of building blocks with abstraction facilitate the creation of a more uniform, consistent and therefore reliable system.
	\item The "change of level" is used in the context in which the system building block decomposition it's not a building block but a sub-system instead. So changing level means changing from the building block level to the system level.
	\item Macro-architecture covers the spectrum of the "large scale" (high level of abstraction)architecture, whereas the micro-architecture covers the spectrum of the building blocks so a lower level of abstraction.
	\item The transition between micro and macro architecture can be seen when recursively decomposing the building block of the system we encounter non-fundamental system-building blocks with a low level of abstraction.
	\item Architectural views are a mean that enable to focus on a specific problem at an appropriate time or to separate different aspects of the architecture of a system from one another. Architectural views differ from one another in a way that each of them depict a specific abstraction of the architecture of a system. The purpose of distinguishing them is that stakeholders that are interested on a specific view, don't have the need to understand all the parts of the architecture but they can laser focus their attention on that particular aspect.
	\item An architectural styles are a pattern of a structural organisation of a family of systems. They primarily reflect the fundamental structure of a software system and its properties. Architectural styles differentiate themselves from architectural patterns for the fact that they have different forms of description. \cite{Vogel:aa}
\end{itemize}