\chapter{Task 1}
\begin{parlist}
	\item Each case explained:
		\begin{enumerate}
			\item Interface and signature: Interface is the abstraction(non implementation) of a class, whereas the signature is the declaration(non implementation) of a method. \cite{deitel2009java}
			\item Class and component: Using the role phase to differentiate them, a component is a design-time unit whereas a class is an implementation-time unit. Designers speak about components but programmers speak about classes.\cite{stackexchangeThereDifference}
			\item Component and module: Components are usually very small in scope, but modules are composed of components and are of very large scope. \cite{stackexchangeThereDifference}
			\item Cohesion and coupling: Cohesion is a concept intra-modules, instead coupling is a concept inter-modules. \cite{geeksforgeeksSoftwareEngineering}
		\end{enumerate}
		\item Design patterns are usually associated with code level commonalities. It provides various schemes for refining and building smaller subsystems. It is usually influenced by programming language. Some patterns pale into insignificance due to language paradigms. Design patterns are medium-scale tactics that flesh out some of the structure and behaviour of entities and their relationships. While architectural designs are seen as commonality at higher level than design patterns. Architectural patterns are high-level strategies that concerns large-scale components, the global properties and mechanisms of a system.\cite{stackoverflowWhatsDifference} In general architectural designs describe how all the system works and how users of the system interact with the system itself, but different design patterns are usually concerned with how components of the system interact with one and other and multiple design patterns can coexist in a single system, whereas for a system usually one architectural design is chosen. \\ Components are usually the building blocks constituting architectural designs. % TODO Review Task 1.b (components)
		\item The singleton pattern:
			\begin{enumerate}
				\item Ensures that a class has only one instance and provides a global point of access to it. Resolves the problems of polluting the code with global variables and sole instances, resolves many security problems since the singleton class implementation facilitate control on how and when clients access to the class. It's also more flexible than Class operations(for languages like C++). \cite{gamma1995elements}
				\item When establishing via an OOP language a connection to a DB, and every query must be executed atomically, there would be implemented a singleton-style class(e.g a Connection class), every class that need to access the DB has to report to the same Connection Class and access the DB one at a time. \\ When the sole instance should be extensible by subclassing, and clients should be able to use an extended instance without modifying their code. \\ In a software environment where a second instance of a class shouldn't be created a better solution is to make the class itself responsible for keeping track of its sole instance. The class can ensure that no other instance can be created (by intercepting requests to create new objects), and it can provide a way to access the instance. \cite{gamma1995elements}
				\item The singleton design pattern belongs to the branch of Creational design patterns.
			\end{enumerate}
		\item \textbf{Proxy}'s purpose is to provide a surrogate or placeholder for another object to control access to it.\\ The \textbf{Adapter} design pattern converts the interface of a class into another interface clients expect. Adapter lets classes work together that couldn't otherwise because of incompatible interfaces. \\ The \textbf{Bridge} design pattern decouple an abstraction from its implementation so that the two can vary independently. \textbf{Bridge} is very similar to \textbf{Adapter}, but we call it Bridge when you define both the abstract interface and the underlying implementation \\ The \textbf{Facade} design pattern purpose is to provide a unified interface to a set of interfaces in a subsystem. Facade defines a higher- level interface that makes the subsystem easier to use.\cite{stackoverflowProxyDecorator}\cite{gamma1995elements}
\end{parlist}